Prag Bat

### 2020-02-11 analysis/data_processing.Rmd
first draft second round

---
title: "Data Processing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(psych)
library(readODS)
library(brms)

@@

```{r}
data%>%
  group_by(subage)%>%
  summarise(n= length(unique(id)))

@@

```{r}
data %>%
  group_by(subage,id)%>%
  summarise(testdays = length(unique(test_day)))%>%
  filter(testdays == 2)%>%
  summarise(complete_retest_data = length(id))
```

```{r}
data %>%
  group_by(id,test_day)%>%
  summarise(n())%>%
  arrange(id,test_day)

@@

```{r}
data%>%
  group_by(test_day,task)%>%
  summarise(n= length(unique(id)))
```

@@

ggplot()+
  geom_hline(yintercept = .5, lty = 2)+
  geom_line(data = p2,aes(x = subage, y = mean, group = task), alpha = .5)+
  geom_jitter(data = p1, aes(x = subage, y = mean, col = subage), alpha = .5, width = .2, height = .01)+
  geom_pointrange(data = p2, aes(x = subage, y = mean, ymin = ci_lower, ymax = ci_upper, col = subage))+
  facet_wrap(~task)+
  labs(x = "Age Group", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  theme_few()+
  theme(legend.position = c(.85,.2))
```

```{r}
p12 <- data%>%
  group_by(id,age,task)%>%
  filter(task != "training")%>%
  summarise(mean = mean(correct))

ggplot(data = p12, aes(x = age, y = mean))+
  geom_hline(yintercept = .5, lty = 2)+
  geom_jitter(alpha = .5, width = .2, height = .01)+
  geom_smooth(method = "glm")+
  facet_grid(~task)+
  labs(x = "Age", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  theme_few()+
  theme(legend.position = c(.85,.2))+
  coord_fixed(ratio = 2)
```
# Models

@@

cs_ts

summary(card_sorting_model1)

@@

inf_model1 <- brm(correct ~ z_age + trial + (trial|id),
                    data = inf_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/inf_model1.rds")

inf_model2 <- brm(correct ~ trial + (trial|id),
                    data = inf_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/inf_model2.rds")

@@

inf_ts

summary(inf_data_model1)

@@

me_model1 <- brm(correct ~ z_age + trial + (trial|id),
                    data = me_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/me_model1.rds")

me_model2 <- brm(correct ~ trial + (trial|id),
                    data = me_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/me_model2.rds")

@@

me_ts

summary(me_model1)

```
## Novelty

@@

nov_model1 <- brm(correct ~ z_age + trial + (trial|id),
                    data = nov_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/nov_model1.rds")

nov_model2 <- brm(correct ~ trial + (trial|id),
                    data = nov_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/nov_model2.rds")

@@

nov_ts

summary(nov_model1)

```
# Visualizing individual tasks

```{r}
# Files to plot data means
p_data <- data %>%
  filter(task != "training")%>%
  mutate(subage = as.numeric(as.character(subage)))%>%
  group_by(task, age,subage,id) %>%
  summarise(correct = mean(correct))

@@

## combine files
samples <- bind_rows(
  samples_cs,
  samples_inf,
  samples_me,
  samples_nov
)

@@

maps <- bind_rows(
  map_cs,
  map_inf,
  map_me,
  map_nov
)

ggplot() +
  geom_hline(yintercept = .5, lty=2, size = 1)+
  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
  geom_line(data = maps, aes(x = age, y = y), size = 1)+
  geom_jitter(data = p_data,aes(x = age, y= correct), width = .00, height = .01, alpha = .2)+
  geom_pointrange(data = p_data2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .5, position = position_dodge(width = .2), pch = 5, col = "#6866cc")+
  labs(x="Age",y="Proportion correct")+
  facet_wrap(~task, nrow = 2)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F, col = F)+
  coord_fixed(ratio = 2)
```

```{r}
p3 <- data%>%
  filter(task != "training")%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  na.omit()

@@

```{r}
reli <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

reli
```

```{r}
reli_age <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(subage, id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(subage,task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

reli_age
```

@@

```{r}
library(psy)

fa_data <- p1 %>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id, -subage)%>%
  na.omit()

@@

fit <- factanal(fa_data, 2, rotation="varimax")

scree.plot(fit$correlation)

fit$loadings

@@

plot(pca)

>>>>

---
title: "Prag Bat"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(psych)
library(readODS)
library(brms)
library(psy)

@@

# Total sample size

```{r}
data%>%
  group_by(subage)%>%
  summarise(n= length(unique(id)))%>%
  kable()

@@

# Sample size with two test days

```{r}
data %>%
  group_by(subage,id)%>%
  summarise(testdays = length(unique(test_day)))%>%
  filter(testdays == 2)%>%
  summarise(complete_retest_data = length(id))%>%
  kable()
```

```{r}
# data %>%
#   group_by(id,test_day)%>%
#   summarise(n())%>%
#   arrange(id,test_day)

@@

```{r}
# data%>%
#   group_by(test_day,task)%>%
#   summarise(n= length(unique(id)))
```

# Results by task binned by year

@@

ggplot()+
  geom_hline(yintercept = .5, lty = 2)+
  geom_line(data = p2,aes(x = subage, y = mean, group = task), alpha = .5)+
  geom_jitter(data = p1, aes(x = subage, y = mean, col = subage), alpha = .5, width = .2, height = .01)+
  geom_pointrange(data = p2, aes(x = subage, y = mean, ymin = ci_lower, ymax = ci_upper, col = subage))+
  facet_wrap(~task)+
  labs(x = "Age Group", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  theme_few()+
  theme(legend.position = c(.85,.2))
```
# Models

@@

cs_ts%>%
  kable()

#summary(card_sorting_model1)

@@

# inf_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = inf_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/inf_model1.rds")
# 
# inf_model2 <- brm(correct ~ trial + (trial|id),
#                     data = inf_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/inf_model2.rds")

@@

inf_ts%>%
  kable()

#summary(inf_data_model1)

@@

# me_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = me_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/me_model1.rds")
# 
# me_model2 <- brm(correct ~ trial + (trial|id),
#                     data = me_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/me_model2.rds")

@@

me_ts%>%
  kable()

#summary(me_model1)

## Novelty

@@

# nov_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = nov_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/nov_model1.rds")
# 
# nov_model2 <- brm(correct ~ trial + (trial|id),
#                     data = nov_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/nov_model2.rds")

@@

nov_ts%>%
  kable()

#summary(nov_model1)

## Preference

pref_data <- data %>%
  filter(task == "preference")

pref_model_data <- pref_data %>%
  mutate(trial = trial - mean(trial))

# pref_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = pref_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/pref_model1.rds")
# 
# pref_model2 <- brm(correct ~ trial + (trial|id),
#                     data = pref_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/pref_model2.rds")

pref_model1 <-readRDS("../saves/pref_model1.rds")

pref_model2 <-readRDS("../saves/pref_model2.rds")

pref_ts <- loo_compare(pref_model1, pref_model2, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, pref_model1 = "correct ~ age + trial + RE", 
                   pref_model2 = "correct ~ trial + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Model, WAIC, SE, weight)

pref_ts%>%
  kable()

#summary(pref_model1)

# Visualizing predictor for age and trial

library(ggridges)

x <- bind_rows(
  posterior_samples(card_sorting_model1, "^b")%>%
  select(-b_Intercept)%>%
  mutate(task = "1 card_sorting"),
  posterior_samples(inf_model1, "^b")%>%
  select(-b_Intercept)%>%
  mutate(task = "4 informativeness"),
  posterior_samples(nov_model1, "^b")%>%
  select(-b_Intercept)%>%
  rename(b_age = b_z_age)%>%
  mutate(task = "2 novelty"),
  posterior_samples(me_model1, "^b")%>%
  select(-b_Intercept)%>%
  rename(b_age = b_z_age)%>%
  mutate(task = "3 mutual_exclusivity"),
  posterior_samples(pref_model1, "^b")%>%
  select(-b_Intercept)%>%
  rename(b_age = b_z_age)%>%
  mutate(task = "0 preference")
)%>%
  gather(estimate, value, -task)

ggplot(x, aes(y = task, x = value, fill = factor(stat(quantile))))+
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE,
    quantiles = c(0.025, 0.975)
  ) +
  facet_grid(~estimate, scales = "free_x")+
  geom_vline(xintercept = 0, col = "grey", lty = 2)+
  scale_fill_manual(values = c("white", "lightblue", "white"))+ 
  guides(fill = F)+
  theme_few()

# Results by task continous

```{r, cache = T}
# Files to plot data means
p_data <- data %>%
  filter(task != "training")%>%
  mutate(subage = as.numeric(as.character(subage)))%>%
  group_by(task, age,subage,id) %>%
  summarise(correct = mean(correct))

@@

## preference

samples_pref <- posterior_samples(pref_model1, "^b")%>%
  mutate(sample = 1:length(b_z_age))%>%
  filter(sample %in% samples_to_draw)%>%
  expand_grid(data$z_age)%>%
  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
         age = `data$z_age` + mean(data$age),
         task = "preference")

## combine files
samples <- bind_rows(
  samples_cs,
  samples_inf,
  samples_me,
  samples_nov,
  samples_pref
)

@@

## preference
map_pref <- tibble(
  age = data$z_age,
  int = fixef(pref_model1)[1,1],
  slope = fixef(pref_model1)[2,1]
)%>%
  mutate(y = plogis(int + slope * age),
         age = age + mean(data$age),
         task = "preference")

maps <- bind_rows(
  map_cs,
  map_inf,
  map_me,
  map_nov,
  map_pref
)

ggplot() +
  geom_hline(yintercept = .5, lty=2, size = 1)+
  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
  geom_line(data = maps, aes(x = age, y = y), size = 1)+
  geom_jitter(data = p_data,aes(x = age, y= correct), width = .00, height = .01, alpha = .2)+
  geom_pointrange(data = p_data2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .5, position = position_dodge(width = .2), pch = 5, col = "#6866cc")+
  labs(x="Age",y="Proportion correct")+
  facet_wrap(~task, nrow = 1)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F, col = F)+
  coord_fixed(ratio = 2)#+
  #ggsave("../graphs/task_results.png", width = 10, height = 2.5, scale = 1.2)
```

# Reliability

## Plot
```{r}
p3 <- data%>%
  filter(task != "training")%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  na.omit()

@@

## Table
```{r}
reli <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

reli%>%
  kable()
```

```{r}
# reli_age <- data%>%
#   filter(task != "training")%>%
#   droplevels()%>%
#   group_by(subage, id,task, test_day)%>%
#   summarise(mean = mean(correct))%>%
#   spread(test_day, mean)%>%
#   na.omit()%>%
#   rename("Day1" = `1`,
#          "Day2" = `2`)%>%
#   group_by(subage,task)%>%
#   summarize(reli = cor.test(Day1,Day2)$estimate,
#             lci = cor.test(Day1,Day2)$conf.int[1],
#             uci = cor.test(Day1,Day2)$conf.int[2],
#             p = cor.test(Day1,Day2)$p.value)%>%
#   mutate_if(is.numeric, round, digits = 2)
# 
# 
# reli_age
```

# Overview: reliability and bi-variat correlations

@@

# Factor analysis

```{r}
fa_data <- p1 %>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id, -subage)%>%
  na.omit()

@@

#fit <- factanal(fa_data, 2, rotation="varimax")

#scree.plot(fit$correlation)

#fit$loadings

@@

#plot(pca)
